### 2022-03-16 CV/cv-sections/papers.tex
cv update

\cventry
{Adil Salim, Laurent Condat, Dmitry Kovalev, Peter Richtárik} % Authors
{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} % Title
{\href{https://arxiv.org/abs/2102.11079}{arXiv 2021}} 
{22 Feb 2021} % Date
{}

@@

\cventry
{Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtárik} % Authors
{IntSGD: Floatless Compression of Stochastic Gradients} % Title
{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}} 
{16 Feb 2021} % Date
{}

>>>>

\cventry
{Adil Salim, Laurent Condat, Dmitry Kovalev, Peter Richtárik} % Authors
{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} % Title
{\href{http://aistats.org/aistats2022/accepted.html}{AISTATS 2022}}
%{\href{https://arxiv.org/abs/2102.11079}{arXiv 2021}} 
{22 Feb 2021} % Date
{}

@@

\cventry
{Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtárik} % Authors
{IntSGD: Floatless Compression of Stochastic Gradients} % Title
{\href{https://openreview.net/forum?id=pFyXqxChZc}{ICLR 2022}}
{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}} 
{16 Feb 2021} % Date
{}
